---
title: "Practical Assignment 2 - Web and Text mining"
author: "João Pires, Vanessa Silva"
date: "30 de Abril de 2017"
output: html_document
---
<br /> 

This report follows the analysis of [IMDB](http://www.imdb.com) movies and their reviews, is the retrieval of relevant information on movies and the analysis of the reviews (and respective scores) assigned by users of the site to the movies.
For this we will use our knowledge regarding web and text mining.

*Web Mining* consists of extracting information from the content of the pages, their links, and users' browsing logs, using data mining tools. 
Thus, we can divide Web Mining into three variants: Web Content Mining; Web Structure Mining; And Web Usage Mining.

*Text Mining* consists of extracting useful information from a collection of documents.
Involves basic pre-processing/text mining operations, such as identification/extraction of representative features, and identification of complex patterns as, e.g. relationships between previously identified concepts.
Text Mining exploits techniques/methodologies from data mining, machine learning, information retrieval, and corpus-based computational linguistics. Where corpus is a collection of documents.


**The Goal**

To use web and text mining to extract and study important informations in the movies and their reviews, of IMDB website.


##Necessary Packages

```{r, eval=FALSE, message=FALSE, warning=FALSE, results='hide'}
#Install the necessary packages
install.packages("rvest")

```


```{r, message=FALSE, warning=FALSE}
#Load the necessary packages
library(rvest)

```


##Tasks

###Find basic information

###Obtain the information on all reviews from a movie

###Model to predict the grade

####Build a data set for learning

####Try a few prediction models and draw conclusions

###Summarise the reviews of a movie